---
title: "Stat 109 Final Project"
author: "Joanna Guo/Austin Nguyen/Jeremiah Rodriguez/Tiffany Huang"
date: "5/4/2019"
output: pdf_document
---

### Create Functions
```{r}
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
subset_colclasses <- function(DF, colclasses="numeric") {
  DF[,sapply(DF, function(vec, test) class(vec) %in% test, test=colclasses)]
}

```

### Source libraries and Read in data
```{r}
packages <- c("ggplot2", "tidyverse", "dplyr","lubridate","knitr","magrittr","moderndive","sqldf","readr","lubridate","car","fastDummies")
ipak(packages)

## Read in Data
## need to install tidyverse in order to get data that is saved as .csv.gz
## tidyverse also has a number of other packages for data wrangling

# Load Data
listings_data = read_csv("http://data.insideairbnb.com/united-states/ma/boston/2019-02-09/data/listings.csv.gz")
#calendar_data = read_csv("http://data.insideairbnb.com/united-states/ma/boston/2019-02-09/data/calendar.csv.gz")
#reviews_data = read_csv("http://data.insideairbnb.com/united-states/ma/boston/2019-02-09/data/reviews.csv.gz")
#glimpse(listings_data)

```

## Below is Original Set of variables, plus some original variables in the dataset
```{r}
#loads libraries
library(readr) #to recode columns from factors to numeric
library(dplyr)
library(lubridate) #needed to handle dates easily 
library(car) #needed to recode values easily

#loads dataset
#cal_detail <- read.csv("calendar_detailed_boston.csv",stringsAsFactors = FALSE,header=TRUE) 
#list_detail <- read.csv("listings_detailed_boston.csv",stringsAsFactors = FALSE,header=TRUE) 

#renames id to listing_id so there is a unique_key on which datasets can be merged
#  names(list_detail)[names(list_detail) == "id"] <- "listing_id"
list_detail = listings_data
names(list_detail)[names(list_detail) == "id"] <- "listing_id"

#defines variables of interest out of total
myvars <- c("listing_id",
            "host_since",
            "host_location",
            "host_response_time",
            "host_response_rate",
            "host_acceptance_rate",
            "host_is_superhost",
            "host_neighbourhood",
            "host_listings_count",
            "host_total_listings_count",
            "host_verifications",
            "host_has_profile_pic",
            "host_identity_verified",
            "neighbourhood_cleansed",
            "property_type",
            "room_type",
            "accommodates",
            "bathrooms",
            "bedrooms",
            "beds",
            "bed_type",
            "square_feet",
            "price",
            "weekly_price",
            "monthly_price",
            "security_deposit",
            "cleaning_fee",
            "guests_included",
            "extra_people",
            "minimum_nights",
            "maximum_nights",
            "minimum_minimum_nights",
            "maximum_minimum_nights",
            "minimum_maximum_nights",
            "maximum_maximum_nights",
            "minimum_nights_avg_ntm",
            "maximum_nights_avg_ntm",
            "calendar_updated",
            "has_availability",
            "availability_30",
            "availability_60",
            "availability_90",
            "availability_365",
            "calendar_last_scraped",
            "number_of_reviews",
            "number_of_reviews_ltm",
            "first_review",
            "last_review",
            "review_scores_rating",
            "review_scores_accuracy",
            "review_scores_cleanliness",
            "review_scores_checkin",
            "review_scores_communication",
            "review_scores_location",
            "review_scores_value",
            "requires_license","license",
            "jurisdiction_names",
            "instant_bookable",
            "is_business_travel_ready",
            "cancellation_policy",
            "require_guest_profile_picture",
            "require_guest_phone_verification",
            "calculated_host_listings_count",
            "calculated_host_listings_count_entire_homes",
            "calculated_host_listings_count_private_rooms",
            "calculated_host_listings_count_shared_rooms",
            "reviews_per_month"
            ## for character counts later 
            ,"name" , 
            "summary" , 
            "space" , 
            "description" , 
            "experiences_offered" , 
            "neighborhood_overview" , 
            "notes" , 
            "transit" , 
            "access", 
            "interaction" , 
            "house_rules"
            )

#applies filters to th Airbnb listing dataset
list_filtered <- list_detail[myvars]

```


### removes spaces in certain variables 
```{r}
#removes spaces in certain variables 
list_filtered$neighbourhood_cleansed <- gsub(" ", "_", list_filtered$neighbourhood_cleansed)
list_filtered$host_response_time <- gsub(" ", "_", list_filtered$host_response_time)
#list_filtered$host_response_time <- gsub("/", "_", list_filtered$host_response_time)
list_filtered$bed_type <- gsub(" ", "_", list_filtered$bed_type)
#list_filtered$bed_type <- gsub("-", "_", list_filtered$bed_type)
list_filtered$property_type <- gsub(" ", "_", list_filtered$property_type)
list_filtered$property_type <- gsub("/", "_", list_filtered$property_type)
list_filtered$room_type <- gsub(" ", "_", list_filtered$room_type)
#list_filtered$room_type <- gsub("/", "_", list_filtered$room_type)

list_filtered$name <- gsub(" ", "_", list_filtered$name)
list_filtered$name <- gsub("/", "_", list_filtered$name)

list_filtered$summary <- gsub(" ", "_", list_filtered$summary)
list_filtered$summary <- gsub("/", "_", list_filtered$summary)

list_filtered$space <- gsub(" ", "_", list_filtered$space)
list_filtered$space <- gsub("/", "_", list_filtered$space)

list_filtered$description <- gsub(" ", "_", list_filtered$description)
list_filtered$description <- gsub("/", "_", list_filtered$description)

list_filtered$experiences_offered <- gsub(" ", "_", list_filtered$experiences_offered)
list_filtered$experiences_offered <- gsub("/", "_", list_filtered$experiences_offered)

list_filtered$neighborhood_overview <- gsub(" ", "_", list_filtered$neighborhood_overview)
list_filtered$neighborhood_overview <- gsub("/", "_", list_filtered$neighborhood_overview)

list_filtered$notes <- gsub(" ", "_", list_filtered$notes)
list_filtered$notes <- gsub("/", "_", list_filtered$notes)

list_filtered$transit <- gsub(" ", "_", list_filtered$transit)
list_filtered$transit <- gsub("/", "_", list_filtered$transit)

list_filtered$access <- gsub(" ", "_", list_filtered$access)
list_filtered$access <- gsub("/", "_", list_filtered$access)

list_filtered$interaction <- gsub(" ", "_", list_filtered$interaction)
list_filtered$interaction <- gsub("/", "_", list_filtered$interaction)

list_filtered$house_rules <- gsub(" ", "_", list_filtered$house_rules)
list_filtered$house_rules <- gsub("/", "_", list_filtered$house_rules)

```

### recodes 'N/A' to NAs
```{r}
#recodes 'N/A' to NAs
list_filtered$host_response_rate[list_filtered$host_response_rate=="N/A"] <- NA
list_filtered$host_response_time[list_filtered$host_response_time=="N/A"] <- NA
list_filtered$host_acceptance_rate[list_filtered$host_acceptance_rate=="N/A"] <- NA ### all of these values are NA
```

### converts price variables from factors into ints
```{r}
list_filtered$price <- parse_number(list_filtered$price)
list_filtered$weekly_price <- parse_number(list_filtered$weekly_price)
list_filtered$monthly_price <- parse_number(list_filtered$monthly_price)
list_filtered$security_deposit <- parse_number(list_filtered$security_deposit)
list_filtered$cleaning_fee <- parse_number(list_filtered$cleaning_fee)
list_filtered$extra_people <- parse_number(list_filtered$extra_people)
list_filtered$host_response_rate <- parse_number(list_filtered$host_response_rate)
```

### recodes variables: host_verifcations 1/0
```{r}
##recodes variables as 1/0
#host_verification
list_filtered$host_verification_email <- ifelse(grepl("email", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_identity_manual <- ifelse(grepl("identity_manual", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_phone<- ifelse(grepl("phone", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_reviews<- ifelse(grepl("reviews", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_jumio<- ifelse(grepl("jumio", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_government_id<- ifelse(grepl("government_id", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_work_email<- ifelse(grepl("work_email", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_selfie<- ifelse(grepl("selfie", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_facebook<- ifelse(grepl("facebook", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_google<- ifelse(grepl("google", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_kba<- ifelse(grepl("kba", list_filtered$host_verifications, ignore.case = T), 1,0)
list_filtered$host_verification_weibo<- ifelse(grepl("weibo", list_filtered$host_verifications, ignore.case = T), 1,0)
```

### other features: recode to 1/0
```{r}
#other features: recode to 1/0
list_filtered$host_is_superhost<- ifelse(grepl("t", list_filtered$host_is_superhost, ignore.case = T), 1,0)
list_filtered$host_has_profile_pic<- ifelse(grepl("t", list_filtered$host_has_profile_pic, ignore.case = T), 1,0)
list_filtered$host_identity_verified<- ifelse(grepl("t", list_filtered$host_identity_verified, ignore.case = T), 1,0)
list_filtered$has_availability<- ifelse(grepl("t", list_filtered$has_availability, ignore.case = T), 1,0)
list_filtered$requires_license<- ifelse(grepl("t", list_filtered$requires_license, ignore.case = T), 1,0)
list_filtered$require_guest_profile_picture<- ifelse(grepl("t", list_filtered$require_guest_profile_picture, ignore.case = T), 1,0)
list_filtered$instant_bookable<- ifelse(grepl("t", list_filtered$instant_bookable, ignore.case = T), 1,0)
list_filtered$is_business_travel_ready<- ifelse(grepl("t", list_filtered$is_business_travel_ready, ignore.case = T), 1,0)
list_filtered$require_guest_phone_verification<- ifelse(grepl("t", list_filtered$require_guest_phone_verification, ignore.case = T), 1,0)
```


### converts dates to workable format
```{r}
#converts dates to workable format
list_filtered$calendar_last_scraped <- ymd(list_filtered$calendar_last_scraped)
list_filtered$first_review <- ymd(list_filtered$first_review)
list_filtered$last_review <- ymd(list_filtered$last_review)
list_filtered$host_since <- ymd(list_filtered$host_since)

#feature generation: calculates "life" of listing based on first review and last review
### This step introduced NAs by coercion 
td<- seconds_to_period(as.duration(interval(list_filtered$first_review,list_filtered$last_review))) 
list_filtered$listing_lifetime_proxy<-as.numeric(sprintf('%02d', day(td)))
```


## Check Data=
```{r}
glimpse(list_filtered)
summary(list_filtered)
```

### Recode the calendar_updated columne

```{r}

## My Data set is still called list_filtered
## First find the unique values of calendar_updated
unique(list_filtered$calendar_updated) ## there is a never column 

list_filtered %>%
  group_by(calendar_updated) %>%
  summarise(listings = n_distinct(listing_id))
## 4 have a never, do those listings have availability?

list_filtered %>%
  filter(calendar_updated == "never") %>% head()
## all of these hosts have been hosts since 2015, but only 1 had availability; going to remove these 4 rows.

list_filtered <- list_filtered %>%
  filter(calendar_updated != "never")

## recode
unique(list_filtered$calendar_updated)
# unique(list_filtered$calendar_updated[order(list_filtered$calendar_updated_numeric)])

list_filtered$calendar_updated_numeric = ifelse(list_filtered$calendar_updated == "today", 0
                                                ,ifelse(list_filtered$calendar_updated == "yesterday", 1
                                                        , ifelse(grepl(pattern = " days ago",list_filtered$calendar_updated), as.numeric(gsub(" days ago", "", list_filtered$calendar_updated))
                                                                 ,ifelse(grepl(pattern = " weeks ago",list_filtered$calendar_updated), as.numeric(gsub(" weeks ago", "", list_filtered$calendar_updated))*7
                                                                         , ifelse(grepl(pattern = "a week ago",list_filtered$calendar_updated), 7
                                                                                  , ifelse(grepl(pattern = " week ago",list_filtered$calendar_updated), as.numeric(gsub(" week ago", "", list_filtered$calendar_updated))*7
                                                                                           , as.numeric(gsub(" months ago", "", list_filtered$calendar_updated))*30)
                                                                                  )
                                                                        )        
                                                              )
                                                      )
                                                )


```


##### Creating new features
# New Features for Number of Characters in string
```{r}
subset_colclasses <- function(DF, colclasses="numeric") {
  DF[,sapply(DF, function(vec, test) class(vec) %in% test, test=colclasses)]
}
# this finds the column names of the character columns in the data set
names(subset_colclasses(list_filtered, c("character")))

# This loop also can create the the number of characters in character columns

for(i in names(subset_colclasses(list_filtered, c("character")))){
  list_filtered[[paste(i,'length', sep = "_")]] <- str_length(list_filtered[[i]])
}

## this might have created some NAs so recoding
new_string_names = list_filtered %>%
  select(select_vars(names(list_filtered), ends_with('length', ignore.case = TRUE))) %>%
  names()

## set any NAs to 0, which would imply these variables had no text/data in the columns
list_filtered[new_string_names][is.na(list_filtered[new_string_names])] <- 0

## check the last set of variables to ensure they were created
# unique(data.frame(column_class = unlist(sapply(list_filtered, function(y) class(y)))))

```


## Creating New Features For Days Since Variables: host_since, first_review, last_review

```{r}
# unique(data.frame(column_class = unlist(sapply(list_filtered, function(y) class(y)))))
## Get the date variables 
names(subset_colclasses(list_filtered, c("Date"))) ## subset_colcclassess is up top
# host_since, calendar_last_scraped, first_review, last_review 

# as.numeric(sprintf('%02d', day( 
#   seconds_to_period(as.duration(interval("2015-01-20 09:50:34", "2015-06-20 16:37:07")))
#   )))

## 2 NAs in host_since: will remove
list_filtered = list_filtered %>% 
  filter(!is.na(host_since))

## new variable called host_since_tenure 
list_filtered$host_since_tenure = as.numeric(sprintf('%02d', day( 
  seconds_to_period(as.duration(interval(list_filtered$host_since,list_filtered$calendar_last_scraped)))
  )))


## new variable called: days_since_first_review
## because there are NA's this would imply these are new listings, so going to assign those values with a value not in the data
## like -1
## then will created a dummy variable to indicate whether the listing is a new listing

list_filtered$days_since_first_review = ifelse(is.na(list_filtered$first_review),-1, as.numeric(sprintf('%02d', day( 
  seconds_to_period(as.duration(interval(list_filtered$first_review,list_filtered$calendar_last_scraped)))
  ))))


## new variable called: days_since_last_review
## because there are NA's this would imply these are new listings, so going to assign those values with a value not in the data
## like -1
## then will created a dummy variable to indicate whether the listing is a new listing

list_filtered$days_since_last_review = ifelse(is.na(list_filtered$last_review),-1, as.numeric(sprintf('%02d', day( 
  seconds_to_period(as.duration(interval(list_filtered$last_review,list_filtered$calendar_last_scraped)))
  ))))

## new variable to indicate if listingis new 

list_filtered$is_new_listing = ifelse(is.na(list_filtered$last_review) & is.na(list_filtered$first_review), 1, 0)


```

## New Feature: Get a total count of the number of properites listed in the neighborhood where the AIRBNB is located: more properties = more supply
```{r}
list_filtered %>% group_by(neighbourhood_cleansed) %>% mutate(count = n())
names(subset_colclasses(list_filtered, c("character")))
unique(list_filtered$neighbourhood_cleansed)
list_filtered = merge(list_filtered, 
      list_filtered %>% group_by(neighbourhood_cleansed) %>% summarise(num_properties_in_neighborhood = n()) )
```

## New Feature: Host is local - boolean does the host neighborhood contain Massachusetts
```{r}
list_filtered$host_is_local<- ifelse(grepl("Massachusetts", list_filtered$host_location, ignore.case = T), 1,0)
```


### REMOVE THIS CODE!!! Box plot of outliers and remove outliers
```{r }
#OUTLIERS: Removes outliers for price 
list_filtered %>%
 ggplot(.,aes(x = price)) + geom_histogram(binwidth = 200)
price_outliers <- boxplot(list_filtered$price)$out #pulls rows of outliers
list_filtered <- list_filtered[-which(list_filtered$price %in% price_outliers),] #filters out outliers 
dim(list_filtered)

#OUTLIERS: Removes outliers for reviews 
# boxplot(list_df_clean$review_scores_rating) #clearly shows outliers
list_filtered %>%
 ggplot(.,aes(x = review_scores_rating)) + geom_histogram()
review_rating_outliers <- boxplot(list_filtered$review_scores_rating)$out #pulls rows of outliers 
list_filtered <- list_filtered[-which(list_filtered$review_scores_rating %in% review_rating_outliers),] #filters out outliers
dim(list_filtered)
```


```{r}
text_decomp <- read.csv("final_text_decomposition.csv",stringsAsFactors = FALSE,header=TRUE) 
df <- merge(list_filtered,text_decomp,by='listing_id')

#df %>% select(everything()) %>%  # replace to your needs summarise_all(funs(sum(is.na(.))))
#treatment of dates specifically 
df$last_review[is.na(df$last_review)] <- as.Date(0,origin="2000-01-01")
df$first_review[is.na(df$first_review)] <- as.Date(0,origin="2000-01-01")
df$calendar_last_scraped[is.na(df$calendar_last_scraped)] <- as.Date(0,origin="2000-01-01")
df$host_since[is.na(df$host_since)] <- as.Date(0,origin="2000-01-01")
#changes all NAs to 0
df[is.na(df)] <- 0
#drops the followings columns: 
#host_verifications (recoded as T/F dummies)
#name, summary, space, description, neighborhood_overview, notes, access,interaction, house_rules because textual features have been generated
#calendar updated because we generated to numeric
df2 <- subset(df,select = -c(host_location, host_neighbourhood,last_review,first_review,calendar_last_scraped,host_since,host_acceptance_rate,experiences_offered_length,experiences_offered,host_acceptance_rate_length,jurisdiction_names,license,calendar_updated, host_verifications,name, summary, space, description, neighborhood_overview, notes, access,interaction, house_rules,transit)) #removes original variables from which dummies were created
names(df2)
#removes / and special characters before dummies are created
df2$property_type <- gsub("/", "_", df2$property_type)
df2$room_type <- gsub("/", "_", df2$room_type)
df2$bed_type <- gsub("-", "_", df2$bed_type)
#creates one infinite value as 0 
df2$cc_avg_reviews[is.infinite(df2$cc_avg_reviews)] <- 0
results <- fastDummies::dummy_cols(df2)
fit1<- lm(price~.,data=results)
summary(fit1)

```